Detecting Bias in Peremptory Challenges Using Historical Strike Data

### 2021-09-14 analysis/paper_draft.Rmd
updated main draft

```{r simltns, echo=FALSE,fig.cap="simultaneous case"}
library(dplyr)
library(ggplot2)
#library(conflicted)
#conflict_prefer("select", "dplyr")
#conflict_prefer("filter", "dplyr")
load_path_b1 <- here::here("b1.csv")
load_path_b2 <- here::here("b2.csv")
load_path_b3 <- here::here("b3.csv")

>>>>

```{r simltns, echo=FALSE,fig.cap="simultaneous case"}

library(dplyr)
library(ggplot2)
#library(conflicted)
#conflict_prefer("select", "dplyr")
#conflict_prefer("filter", "dplyr")

# ADD SCRIPT FOR GENERATING b1.csv, b2.csv, b3.csv

load_path_b1 <- here::here("b1.csv")
load_path_b2 <- here::here("b2.csv")
load_path_b3 <- here::here("b3.csv")
